SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
oops

Cross-site request forgery attacks typically involve just a
URL or page that contains a malicious request towards
a site vulnerable to {\sc csrf}.
An attacker can entice a victim to click on the URL or visit the page
through social engineering ({\sc csrf} 1), which will the result in a malicious
request towards the vulnerable site ({\sc csrf} 2}).
Note that this scenario does not involve the injection of any code through the
exploitation of some server-side vulnerability (as is the case with Server 1).
On the other hand, {\sc csrf} is also possible through injection
({\sc i-csrf}). In this attack, an attacker
manages to inject {\sc html} code that contains
a malicious {\sc csrf} request in the way we described in
Section~\ref{sec:attacks}.
This code will be stored
in the database ({\sc i-csrf} 5)
and then it will re-enter the application when
a user visits a page ({\sc i-csrf} 6). When the
content reaches the browser, a malicious request will be generated
towards the site that is vulnerable to {\sc csrf}.

>>>>

Cross-site request forgery attacks typically involve just a
URL or page that contains a malicious request towards
a site vulnerable to {\sc csrf}.
An attacker can entice a victim to click on the URL or visit the page
through social engineering ({\sc csrf} 1), which will the result in a malicious
request towards the vulnerable site ({\sc csrf} 2).
Note that this scenario does not involve the injection of any code through the
exploitation of some server-side vulnerability (as is the case with Server 1).
On the other hand, {\sc csrf} is also possible through injection
({\sc i-csrf}). In this attack, an attacker
manages to inject {\sc html} code that contains
a malicious {\sc csrf} request in the way we described in
Section~\ref{sec:attacks}.
This code will be stored
in the database ({\sc i-csrf} 5)
and then it will re-enter the application when
a user visits a page ({\sc i-csrf} 6). When the
content reaches the browser, a malicious request will be generated
towards the site that is vulnerable to {\sc csrf}.
